The Astropy Project

### 2017-11-13 main.tex
infrastructure

\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate. The the values for each parameter in the model set must be passed as iterables of size \texttt{n_models}. This creates a model set that can be efficiently evaluated. Model sets are most useful for efficiently fitting multiple linear models of the same kind.

@@

Modeling also supports a plugin system for fitters, which allows using the
\astropypk models with external fitters. An example of this is
\package{SABA}\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
Sherpa\footnote{\url{http://cxc.cfa.harvard.edu/contrib/sherpa/}}
and \package{astropy.modeling}, to bring the Sherpa fitters into \astropypkg.

@@

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
%\inlinecomment{BMS}{should we use links to the appropriate github repo?}
%\inlinecomment{PLL}{IMHO a list of GitHub repo links for affil. pkgs. should be in appendix, if included.}
\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
%
\par In addition to astronomy related packages and libraries, the \astropy
Project also maintains and distributes several generic purpose infrastructure packages.
The following sections describes the most widely used selection of them.
%
\subsection{Package template}
% Brigitta may write this up if there is no other takers
%
\par \astropy provides the \package{package-template}\footnote{\url{https://github.com/astropy/package-template/}}
package. Using this template, any \python package can make use of the ready-to-go package
layout, setup, installation and documentation infrastructure developed originally for the
\astropypkg core package and affiliated packages maintained by the \astropy. It also provides
a testing framework, CI templates and configurations, Cython integration, and documentation
on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
%
\package{ci-helpers}\footnote{\url{https://github.com/astropy/ci-helpers}} is a
collection of scripts that empowers package maintainers to control their testing
set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the \astropy ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for Travis CI and Appveyor CI.
%
\subsection{Sphinx extensions}

The documentation for many \python packages the core \package{astropy} package
as well as for all packages in the Astropy ecosystem is written using the
Sphinx package. This package makes it possible to write the documentation using
plain text files that follow a markup language called reStructuredText, and
Sphinx can then transform this into HTML or \LaTeX{} documentation. As part of
the project, we have developed a few extensions that facilitate generating
documentation for a large project like Astropy. One of the main extensions we
have developed is
\package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
which makes it easy with a single reStructuredText command to generate a set of
documentation pages listing all the available classes, functions, and
attributes in any given \python module.

@@

% TODO: need to put releases of sphinx-automodapi on Zenodo!

%\inlinecomment{BMS}{What about pytest-astropy, should we inlude it here, or
%  for the future section?}
%\inlinecomment{PLL}{pytest-astropy is v3, right?}
% \section{State of the Ecosystem}
% Commenting out unless a clear statement is added

>>>>

\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate. The the values for each parameter in the model set must be passed as iterables of size \texttt{n\_models}. This creates a model set that can be efficiently evaluated. Model sets are most useful for efficiently fitting multiple linear models of the same kind.

@@

Modeling also supports a plugin system for fitters, which allows using the
\astropypkg models with external fitters. An example of this is
\package{SABA}\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
Sherpa\footnote{\url{http://cxc.cfa.harvard.edu/contrib/sherpa/}}
and \package{astropy.modeling}, to bring the Sherpa fitters into \astropypkg.

@@

\section{Infrastructure for Astropy affiliated packages}

\label{sec:infrastructure}
\inlinecomment{BMS}{should we describe astropy-helpers even though it's future is unsure?}
% Text also edited by Adrian PW

In addition to astronomy-specific packages and libraries, the \astropy Project
also maintains and distributes several general-purpose infrastructure packages
that help with the maintenance and upkeep of the \astropypkg core package and
other affiliated packages.
The following sections describes the most widely-used infrastructure packages
developed by the \astropy Project.

\subsection{Package template}
% Brigitta may write this up if there is no other takers

\astropy provides a package template --- as a separate \github repository,
\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-t
emplate/}} --- that aims to simplify setting up packaging, testing, and
documentation builds for developers of affiliated packages or
\astropypkg-dependent packages.
Any \python package can make use of this ready-to-go package layout, setup,
installation, and \package{Sphinx} documentation build infrastructure that was
originally developed for the \astropypkg core package and affiliated packages
maintained by the \astropy project.
The package template also provides a testing framework, template configurations
for continuous integration services, and \package{Cython} build support.

\subsection{Continuous integration helpers}
% Brigitta

\astropy also provides a set of scripts for setting up and configuring
continuous integration (CI) services as a \github repository,
\package{astropy/ci-helpers}\footnote{\url{https://github.com/astropy/ci-helpers}}
These tools aim to empower package maintainers to control their testing set up
and installation process for various continuous integration services through a
set of environment variables.
While the current development is mostly driven by the needs of the \astropy
ecosystem, the actual usage of this package is extremely widespread. The current
tools support configuration for Travis CI and Appveyor CI.

\subsection{Sphinx extensions}

The documentation for many \python packages, the core \astropypkg package, and
for all packages in the \astropy ecosystem is written using the
\package{Sphinx} documentation build system.
\package{Sphinx} makes it possible to write documentation using plain text files
that follow a markup language called ``reStructuredText,'' which are then
transformed into HTML or \LaTeX{} documentation during the documentation build
process.
For the \astropy project, we have developed a few \package{Sphinx} extensions
that facilitate automatically generating API documentation for large projects,
like the \astropypkg core package.
The main extension we have developed is
\package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
which makes it easy with a single reStructuredText command to generate a set of
documentation pages listing all of the available classes, functions, and
attributes in a given \python module.

@@

% \section{State of the Ecosystem}
% Commenting out unless a clear statement is added
